Sparse Word Embeddings for Multi-domain Machine Translation

### 2019-05-02 2019/emnlp/sparse.tex
new

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{naaclhlt2019}
\usepackage{times}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{url}
\usepackage{float} 
\usepackage{tabularx}
\usepackage{xcolor}
\newtheorem{lemma}{Lemma}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{definition}{Definition}[section]
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage[draft]{todo}
\floatname{algorithm}{Procedure}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

@@

\begin{table}[H]
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & & & & & & & & \\
 \hline
 EMEA-finetuned & & & & & & & & \\
 \hline
 EPPS-finetuned & & & & & & & & \\
 \hline
 ECB-finetuned & & & & & & & & \\
 \hline
 Sparse & & & & & & & & \\
 \hline
 Domain Control & & & & & & & & \\
 \hline
 WDCMT (conditional GRU) & 68.76 & 35.71 & 52.75 & 32.03 & 29.81 & 19.58 & 24.63 & 23.28 \\
 \hline 
\end{tabularx}}
\end{center}
\caption{bpe-detokenized BLEU score for Recurrent network architecture on language pair English-French. Notations as same as figure \ref{tab:1} except that other models from WDCMT of \cite{D18-1041} use Bidirectional-LSTM}
\label{tab:3}
\end{table}

\begin{table}[H]
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & & & & & & & \\
 \hline
 EMEA-finetuned & & & & & & & \\
 \hline
 EPPS-finetuned & & & & & & & \\
 \hline
 ECB-finetuned & & & & & & & \\
 \hline
 Sparse & & & & & & & \\
 \hline
 Domain Control & & & & & & & \\
 \hline
 WDCMT (conditional GRU) & & & & & & & \\
 \hline 
\end{tabularx}}
\end{center}
\caption{BLEU scores for RNN architecture on English-German. Notations are the same as for figure~\ref{tab:3}}
\label{tab:4}
\end{table}

@@

\section*{Acknowledgments}
\fyTodo{Homegenize refs - urls, addresses, etc}
\bibliography{naaclhlt2019}
\bibliographystyle{plainnat}

\end{document}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{emnlp-ijcnlp-2019}
\usepackage{times}
\usepackage{latexsym}

\usepackage{url}

%\aclfinalcopy % Uncomment this line for the final submission

\newcommand\BibTeX{B{\sc ib}\TeX}
\newcommand\confname{EMNLP-IJCNLP 2019}
\newcommand\conforg{SIGDAT}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{url}
\usepackage{float} 
\usepackage{tabularx}
\usepackage{xcolor}
\newtheorem{lemma}{Lemma}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{definition}{Definition}[section]
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage[draft]{todo}
\floatname{algorithm}{Procedure}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

@@

\begin{figure}[H]
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 65.42 & 34.7 & 51.38 & 29.27 & 28.95 & 17.82 & 22.21 & 21.63 \\
 \hline
 EMEA-finetuned & & & & & & & & \\
 \hline
 EPPS-finetuned & & & & & & & & \\
 \hline
 ECB-finetuned & & & & & & & & \\
 \hline
 Sparse & 68.51 & 35.75 & 51.19 & 28.88 & 28.92 & 17.89 & 22.73 & 21.08\\
 \hline
 Domain Control & & & & & & & & \\
 \hline
 WDCMT (conditional GRU) & 68.76 & 35.71 & 52.75 & 32.03 & 29.81 & 19.58 & 24.63 & 23.28 \\
 \hline 
\end{tabularx}}
\end{center}
\caption{bpe-detokenized BLEU score for Recurrent network architecture on language pair English-French. Notations as same as figure \ref{tab:1} except that other models from WDCMT of \cite{D18-1041} use Bidirectional-LSTM}
\label{tab:3}
\end{figure}

\begin{figure}[H]
\begin{center}
 \resizebox{\columnwidth}{!}{\begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline
 Mixed & 62.63 & 23.91 & 66.95 & 16.92 & 21.29 & 10.9 & & 14.19 \\
 \hline
 EMEA-finetuned & & & & & & & & \\
 \hline
 EPPS-finetuned & & & & & & & & \\
 \hline
 ECB-finetuned & & & & & & & & \\
 \hline
 Sparse & & & & & & & & \\
 \hline
 Domain Control & & & & & & & & \\
 \hline
 WDCMT (conditional GRU) & & & & & & & & \\
 \hline 
\end{tabularx}}
\end{center}
\caption{BLEU score for Recurrent network on language pair English - German. The notation is same as figure \ref{tab:3}}
\label{tab:4}
\end{figure}

@@

\section*{Acknowledgments}
\fyTodo{Homegenize refs - urls, addresses, etc}
\bibliography{emnlp-ijcnlp-2019}
\bibliographystyle{acl_natbib}
\end{document}
